ForOpenCL: Transformations Exploiting Array Syntax in Fortran for Accelerator Programming

### 2012-04-16 papers/IJCSE/intro.tex

Transformations for arbitrary Fortran procedures are not attempted.
Furthermore, a mechanism to transform the calling site to
automatically invoke OpenCL kernels is not provided at this time.
While it is possible to accomplish this task within ROSE, it is
considered outside the scope of this paper.  However, ForOpenCL
provides via Fortran interfaces a mechanism to call the C OpenCL
runtime and enable Fortran programmers to access OpenCL kernels
generated by the supplied transformations.

>>>>

Transformations for arbitrary Fortran procedures are not attempted.
Furthermore, a mechanism to transform the calling site to
automatically invoke OpenCL kernels is not provided at this time.
While it is possible to accomplish this task within ROSE, it is
considered outside the scope of this paper.  ForOpenCL is a set of
tools providing: 1. Fortran interfaces to the OpenCL runtime library;
2. A wrapper library providing a high-level interface to these direct
calls to C, thus simplifying calling OpenCL kernels for
Fortran Programmers; 3. A code generation facility for transforming
Fortran pure elemental functions to OpenCL kernels.
%However, ForOpenCL
%provides via Fortran interfaces a mechanism to call the C OpenCL
%runtime and enable Fortran programmers to access OpenCL kernels
%generated by the supplied transformations.
